Stage-Splitting a Modal Language

### 2014-10-29 paper/splitting.tex
changes to intro of splitting

The goal of splitting is to take a multistage term,
which may feature interleaved stage \bbone\ and stage \bbtwo\ code,
and untangle it to produce two separate terms:
one with all of the stage \bbone\ content, and one with all of the stage \bbtwo\ content.
The splitting algorithm comes in several forms, depending on the stage of the input and whether it is a value.
The stage \bbtwo\ versions will be addressed first,
before the more complicated stage \bbone\ versions.

In all cases, the outputs of splitting are terms in an unstaged language, \langmono. 
This language is untyped and contains no staging features, 
but otherwise has the same term constructors as \lang. 
It has a evaluation judgment $\redsym$, which works in the expected way to produce unstaged values.

@@

We cover stage \bbtwo\ term splitting first, because it has the most familiar signature.
Splitting takes a term $\coltwo e A$ and produces from it a first stage term
$p$ (called the {\em precomputation}) and a second stage term $l.r$ (called the {\em resumer})
open on a single variable, such that $e$ is equivalent to $\letin l p r$.
Intuitively, the responsibility of $p$ is to produce an intermediate data structure, 
and the responsibility of $r$ is to consume that data structure and produce the same final value as $e$.

>>>>

The goal of splitting is to take a multistage \lang\ term,
which may feature interleaved stage \bbone\ and stage \bbtwo\ code,
and untangle it to produce two separate terms:
one with all of the stage \bbone\ CONTENT, and one with all of
the stage \bbtwo\ CONTENT.

Splitting emits terms in an unstaged language, \langmono, that is 
untyped and contains no staging features, but otherwise has the same term constructors as \lang. 
\langmono\ has a evaluation judgment $\redsym$, which works in the expected way to produce unstaged values.

Since splitting stage \bbtwo\ terms from \lang\ is a simpler operation than splitting stage 1 terms,
we first describe the mechanics of splitting stage \bbtwo, before moving to the more complex
case of stage \bbone\ term splitting.

%The splitting algorithm comes in several forms, depending on the stage of the input and whether it is a value.
%The stage \bbtwo\ versions will be addressed first,
%before the more complicated stage \bbone\ versions.

@@

% We cover stage \bbtwo\ term splitting first, because it has the most familiar signature.

Splitting a stage-2 term $\coltwo e A$ produces a term
$p$ (called the {\em precomputation}) and a term $l.r$ (called the {\em resumer})
open on a single variable, such that $e$ is equivalent to $\letin l p r$.
Intuitively, the responsibility of $p$ is to produce an intermediate data structure, 
and the responsibility of $r$ is to consume that data structure and produce the same final value as $e$.
